---
title: "Weighted regression of Annual Survival"
format: html
editor: visual
---

```{r}
#| message: false
#| warning: false
#load libraries
library(tidyverse, quietly = TRUE)
library(metafor, quietly = TRUE)

#load data
AnnualSurvival<-readRDS("data/AnnualSurvivalRate.RDS")

# Prepare the data
AnnualSurvival$var<-AnnualSurvival$SD^2
AnnualSurvival<-AnnualSurvival |> 
  janitor::clean_names()
names(AnnualSurvival)
```

## Data

```{r}
AnnualSurvival |> 
  mutate(N=numbers_of_birds,
         Mean_Survival=avg,
         Species=species,
         Harvested_population = harvest) |> 
  select(Species, Mean_Survival, sd, N, Harvested_population) |> 
kableExtra::kable() |> 
  kableExtra::kable_styling()
```

## Weighted regression model

Survival estimates combined and weighted by sample size

```{r}
# Weighted regression

mod1<-rma(avg, var, weights =numbers_of_birds, data=AnnualSurvival)

```

```{r}
theme_set(theme_bw(base_size=10))
forrest_data<-rbind(data.frame(ES=mod1$yi,SE=sqrt(mod1$vi),
                               Type="Study",
                               Study=c(paste0("Study", 1:22))),
                    data.frame(ES=mod1$b,SE=mod1$se,Type="Summary",Study="Summary"))

forrest_data$order=c(1:23)
forrest_data
plot1<-ggplot(data=forrest_data,aes(x=reorder(Study, -order),y=ES,ymax=ES+(1.96*SE),ymin=ES-(1.96*SE),size=factor(Type),colour=factor(Type)))+
  geom_pointrange()
plot2<-plot1+
  coord_flip()+
  geom_hline(yintercept=0, lty=2,linewidth=1)+
  scale_size_manual(values=c(0.5,1))
plot3<-plot2+
  xlab("Study")+
  ylab("Survival estimate")+
  scale_colour_manual(values=c("grey","black"))
plot3+theme(legend.position="none")



```

## Estimated Survival

From the weighted regression model we get an mean annual survival of `r round(coef(mod1),2)` , with a lower estimate of `r round(mod1$ci.lb,2)` and an upper estimate of `r round(mod1$ci.ub,2)` .

## Is there a difference with harvested and non-harvested populations?

```{r}
mod2<-rma(avg, var, weights = numbers_of_birds, data=AnnualSurvival, subset= AnnualSurvival$harvest=="Yes")
mod3<-rma(avg, var, weights = numbers_of_birds, data=AnnualSurvival, subset= AnnualSurvival$harvest=="No")

dat.comp <- data.frame(estimate = c(coef(mod2), coef(mod3)), stderror = c(mod2$se, mod3$se),
                       meta = c("Harvest","No harvest"), tau2 = round(c(mod2$tau2, mod3$tau2),3))

(comp_mod<-rma(estimate, sei=stderror, mods = ~ meta, method="FE", data=dat.comp, digits=3))

```

## Is there a difference with the new data?

```{r}
mod4<-rma(avg, var, weights = numbers_of_birds, data=AnnualSurvival[1:11,]) 
mod5<-rma(avg, var, weights = numbers_of_birds, data=AnnualSurvival[12:22,])  
dat.comp <- data.frame(estimate = c(coef(mod4), coef(mod5)), stderror = c(mod4$se, mod5$se),                        meta = c("Old","New"), tau2 = round(c(mod4$tau2, mod5$tau2),3))  

(comp_mod<-rma(estimate, sei=stderror, mods = ~ meta, method="FE", data=dat.comp, digits=3)) 
```
